% Template based on the ILLC's Master of Logic template, 
% then the VUA's Master CS Standard Thesis template. 

\documentclass[11pt]{cltlmathesis}
\usepackage{cltlmathesis} % you can load extra packages in that file or after this line
\usepackage{cltlmatitle}  

\begin{document}
% ----------------------------------
% IMPORTANT NOTE: lines marked with TODO contain filler text that must be replaced appropriately,
% or pointers to example or stub files 


\title{New Insights in Computational Lexicology}  % TODO 
\author{Student name}                             % TODO
\supervisors{Supervisor name(s)}		              % TODO
\reader{2nd reader name}			% 2nd reader        % TODO

% Select the appropriate track/degree             % TODO
\track{Human Language Technology}     		
\degree{Research Master}         		
% OR 
%\track{Text Mining}     		
%\degree{Master}         	

\date{June 27, 2025}  % submission date % TODO

\maketitle
% ----------------------------------
\frontmatter
\include{tex/abstract}        % TODO

% ----------------------------------

\frontchapter{Declaration of Authorship}

I, \@author, declare that this thesis, titled \showtitle\
 and the work presented in it are my own. I confirm that:
\begin{itemize}
\item This work was done wholly or mainly while in candidature for a \@degree degree at this University.
\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
\item Where I have consulted the published work of others, this is always clearly attributed.
\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
\item I have acknowledged all main sources of help.
\item Where the thesis is based on work done by myself jointly with others, I have made
clear exactly what was done by others and what I have contributed myself.
\end{itemize}

\vspace{4cm}

\noindent
Date: $<$date$>$                  % TODO  
\vspace{1cm}

\noindent
Signed: $<$student signature$>$   % TODO 
  
% ----------------------------------

% TODO acknowledgments, list of figures and tables are optional
\include{tex/acknowledgments}
\include{tex/listoffigures} 	
\include{tex/listoftables} 	
\tableofcontents

% ----------------------------------
\mainmatter
\pagestyle{headings}

% TODO Adapt the list of files to be included as needed.
% NOTE You may divide the text body in as many files as you see fit.
% Using one file per chapter generally forms a good trade-off
% between logical division and file length.
\include{tex/introduction}
\include{tex/methodology}
\include{tex/results}
\include{tex/discussion}
\include{tex/conclusion}


% TODO if you need appendices 
\appendix
\include{tex/appendix}

% ----------------------------------
% TODO replace by your own bibliography
\bibliography{bib/example}
\end{document}

